### 2021-11-21 thesis/tex/nsiResults.tex
update

\section{Non-Standard Interactions}\label{sec:nsiResults}
%TODO: add
\subsection{Constraining the NSI parameters}\label{sec:constraining}
In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$ by considering the detectors separately as well as jointly.
For our analyses, we define our $\chi^2$ as
\begin{align}\label{eq:chisq_NSI}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory in bin $\{i,j,k\}$, where $i$ denotes the $\Ereco$ bin, $j$ denotes the $\zreco$ bin,
and $k$ denotes the event-type bin, i.e. track or cascade. 
$N_{ijk}^\text{data}$ is the observed number of events in that bin. $\sigma^\text{data}_{ijk}$ is the experimental uncertainty, and $\sigma^\text{syst}_{ijk}$ the uncorrelated systematic
incertainty.

>>>>

\section{Constraining the NSI parameters}\label{sec:constraining}
In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$ by considering the detectors separately as well as jointly.
For our analyses, we define our $\chi^2$ as
\begin{align}\label{eq:chisq_NSI}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory in bin $\{i,j,k\}$, where $i$ denotes the $\Ereco$ bin, $j$ denotes the $\zreco$ bin,
and $k$ denotes the event-type bin, i.e. track or cascade. 
$N_{ijk}^\text{data}$ is the observed number of events in that bin. $\sigma^\text{data}_{ijk}$ is the experimental uncertainty, and $\sigma^\text{syst}_{ijk}$ the uncorrelated systematic
incertainty.
